---
title: "BMI Calculator"
author: "Yen-Chu Tu"
date: "June 7, 2019"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Body Mass Index

The Body Mass Index is a number that represents the health and the bodyfat of
your body. It's commonly used in the health industry, and it applies to both men
and women. The BMI score can be interpreted by:

*Under Weight: BMI is lower than 18.5

*Normal Weight: BMI is between 18.5 and 24.9

*Over Weight: BMI is between 25 to 29.9

*Obese: BMI is above 30

## Calculations
The Body Mass Index is based on your height and weight. It can be calculated as
the weight of the subject divided by his/her height squared.
```{r}
weight <- 70
height <- 175
BMI <- weight/(height/100)^2
BMI
```
### FOR SHINY EMBEDDED, PLEASE SEE SHINYAPPS.IO LINK IN SUBMISSION

## Target BMI for Your Height

The target BMI for your height is always at 22, center of the Normal Weight
BMI range. It can be found by multiplying 22 by the subject's height squared.
```{r}
Goal <- 22*(height/100)^2
print('Your Target Weight is')
Goal
```

## Conclusion

The App loaded on the Shiny Server is a combination of the BMI calculator and
the target weight calculator. The target weight can be displayed or hidden via
the checkbox input. 

Keep in mind that BMI is by no means a perfect system, and fails to take into 
account the muscle mass and fat mass discrepancies in the body. Atheletes tend 
to have a very high BMI.

Hopefully, this application can help you understand where your weight and health
stands!

